---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trunc

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `trunc` is to provide facilitate generating random variate values, distribution function, density function and quantile function for uni-variate truncated distributions.

The underlying distribution can be any distribution that is available in the namespace. For example, `gompertz` distribution available means that the corresponding `rgompertz`, `dgompertz`, `pgompertz`, `qgompertz` are available. `trunc` utilizes these functions to provide their truncated counterpart.

## Installation

You can install the development version of trunc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gsk-tech/trunc")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(trunc)
## basic example code
```

Density generation:
```{r}
dtrunc(a = 2, dist = "binom", x = 3, args = list(size = 10, prob = 0.2))
```

Random variate generation:
```{r}
rtrunc(n = 10, a = 0, dist = "norm", args = list(mean = 10, sd = 10))
```

Distribution function generation:
```{r}
ptrunc(a = 2, dist = "binom", q = 6, args = list(size = 10, prob = 0.2))
```

Quantile function generation:
```{r}
qtrunc(a = 0, dist = "norm", p = 0.95, args = list(mean = 10, sd = 10))
```
