---
title: "trunc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{trunc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(trunc)
library(survival)
library(flexsurv)
```

Suppose we are fitting a log-logistic distribution to the following time-to-event data:

```{r}
tte_data <- survival::veteran
head(tte_data)
```

We use the `flexsurv` package to do the parametric fitting:

```{r}
tte_fit <- flexsurv::flexsurvreg(Surv(time = time, event = status) ~ . , data = tte_data, dist = "llogis")
```

Using the fitted parameters, suppose we want to simulate the event-time for a subject who was censored, i.e., `status = 0`, given that the subject has already survived till the follow-up time. The censored subjects are:

```{r}
tte_cens_data <- tte_data[tte_data$status==0,]
```

Let's do the simulation for the first subject from the above `tte_cens_data`. This person has already lived `r tte_cens_data$time[1]` time.

First we derive the parameters of `llogis` distribution corresponding to this person:

```{r}
tte_cens_covariate_matrix <- model.matrix(~., data = subset(tte_cens_data, select=-c(time, status))[1,])[, -1]
tte_coef_comb <- tte_cens_covariate_matrix %*% coef(tte_fit)[3:10]
shape = exp(coef(tte_fit)[1] + tte_coef_comb)
scale = exp(coef(tte_fit)[2] + tte_coef_comb)
```
Then we do the truncated simulation as follows:

```{r}
rtrunc(n = 1, a = tte_cens_data$time[1], dist = "llogis", args = list(shape = shape, scale = scale))
```
